### 2005-11-21 doc/EFA/efa.tex
*** empty log message ***

Formally we define the synchronous product $A||B$ of two EFA's
\begin{eqnarray}
A=\langle Q^A, \Sigma^A, \delta^A, q^A_i, Q^A_m, X^{A},
G^A,x^A_0,X^A_m \rangle
\end{eqnarray} and \begin{eqnarray} B=\langle Q^B, \Sigma^B, \delta^B, q^B_i,
Q^B_m, X^{B}, G^B,x^B_0,X^B_m \rangle
\end{eqnarray} as
\begin{eqnarray}
A||B&=&\langle Q^A\times Q^B, \Sigma^A \cup \Sigma^B ,
\delta^{A||B}, (q^A_i,q^B_i) ,\nonumber\\
&& Q^A_m\times Q^B_m, X^A \times X^B, G^{A||B},(x^A_0,x^B_0),
X^A_m \times X^B_m \rangle.
\end{eqnarray}
To define the guard functions, the action functions and the
transition function of the product we make use of the
corresponding functions in $A$ and $B$. To denote the elements of
$A||B$ we remove unnecessary  superscripts and write $A||B=\langle
Q, \Sigma, \delta, q_i, Q_m, X, G ,x_0, X_m \rangle$. The guard
functions $g_{q \sigma}(x)$ are defined as
\begin{eqnarray}\label{guard_sync_1}
g_{q \sigma}(x)=\left\{
\begin{array}{ll}
g_{q^A\sigma}(x^{A})\wedge g_{q^B\sigma}(x^{B}) \quad\quad\sigma\in \Sigma^A \cap \Sigma^B\\
g_{q^A\sigma}(x^{A})\quad\quad\quad\quad\quad\quad\quad\sigma\in \Sigma^A\setminus\Sigma^B\\
g_{q^B\sigma}(x^{B})\quad\quad\quad\quad\quad\quad\quad\sigma\in\Sigma^B\setminus\Sigma^A
\end{array}\right.
\end{eqnarray}
If in any of the three cases, the corresponding guard function is
undefined the guard function for the product $g_{q \sigma}$ is
also undefined. To simplify the notation and increase readability,
we use "dummy" guard functions in the following way. If $\sigma\in
\Sigma^A \setminus \Sigma^B$ we introduce fictional guards
functions $g_{q^B\sigma}(.)=1$ for $B$ and if
$\sigma\in\Sigma^B\setminus \Sigma^A$ we set $g_{q^A\sigma}(.)=1$.
Doing this, we can write equation (\ref{guard_sync_1}) as
\begin{eqnarray}
g_{q \sigma}(x)= g_{q^A\sigma}(x^{A})\wedge g_{q^B\sigma}(x^{B}).
\end{eqnarray}
The updating functions $a_{q \sigma}(x)$ are defined as
\begin{eqnarray}\label{action_sync_1}
a_{q \sigma}(x)=\left\{
\begin{array}{ll}
 \big(a_{q^A \sigma}(x^{A}), a_{q^B \sigma}(x^{B})\big)\quad\quad\sigma\in \Sigma^A \cap \Sigma^B\\
\big(a_{q^A\sigma}(x^{A}),x^{B}\big)\quad\quad\quad\quad\quad\sigma\in\Sigma^A\setminus\Sigma^B\\
\big(x^{A},a_{q^B\sigma}(x^{B})\big)\quad\quad\quad\quad\quad\sigma\in\Sigma^B\setminus\Sigma^A
\end{array}\right.
\end{eqnarray}
As in the definition of the guard functions (\ref{guard_sync_1}),
the notion of being undefined is inherited from the action
functions of $A$ and $B$. Similar to the "dummy" guard functions
we introduce fictional action functions. If $\sigma\in \Sigma^A
\setminus \Sigma^B$ we introduce fictional action functions
$a_{q^B\sigma}(x^B)=x^B$ for $B$ and if
$\sigma\in\Sigma^B\setminus \Sigma^A$ we set
$a_{q^A\sigma}(x^A)=x^A$. With this convention equation
(\ref{action_sync_1}) simplifies to
\begin{eqnarray}
a_{q \sigma}(x)=
 \big(a_{q^A \sigma}(x^{A}), a_{q^B \sigma}(x^{B})\big).
\end{eqnarray}

 The transition function $\delta^{A||B}$ is defined from $\delta^A$ and $\delta^B$ as
\begin{eqnarray}
\delta^{A||B}(q,\sigma,x)=\left\{
\begin{array}{ll}
\big(\delta^A(q^A,\sigma),\delta^B(q^B,\sigma),a_{q \sigma}(x)\big) \quad\quad \sigma\in \Sigma^A \cap \Sigma^B \quad g_{q \sigma}(x)=1\\
\big(\delta^A(q^A,\sigma),q^B,a_{q \sigma}(x)\big) \quad\quad\quad\quad\quad \sigma\in \Sigma^A \setminus \Sigma^B \quad g_{q \sigma}(x)=1\\
\big(q^A,\delta^B(q^B,\sigma),a_{q \sigma}(x)\big) \quad\quad\quad\quad\quad \sigma\in \Sigma^B \setminus \Sigma^A \quad g_{q \sigma}(x)=1\\
\textrm{
undefined}\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
g_{q\sigma}(x)=0
\end{array}\right.
\end{eqnarray}

\subsubsection{Properties of the product}
$(A||B)||C$:

\begin{eqnarray}
g^{(A||B)||C}_{q \sigma}(x)&=& g_{q^{AB}\sigma}(x^{AB})\wedge
g_{q^C\sigma}(x^{C})\nonumber\\
&=&g_{q^A\sigma}(x^{A})\wedge g_{q^B\sigma}(x^{B})\wedge
g_{q^C\sigma}(x^{C})\nonumber\\
&=& g_{q^{A}\sigma}(x^{A})\wedge g_{q^{BC}\sigma}(x^{BC})\nonumber\\
&=& g^{A||(B||C)}_{q \sigma}(x)
\end{eqnarray}

\begin{eqnarray}
a^{(A||B)||C}_{q \sigma}(x)&=&
 \big(a_{q^{AB} \sigma}(x^{AB}), a_{q^{C}
 \sigma}(x^{C})\big)\nonumber\\
&=&\big(a_{q^{A} \sigma}(x^{A}), a_{q^{B}
 \sigma}(x^{B}), a_{q^{C}
 \sigma}(x^{C})\big)\nonumber\\
&=&\big(a_{q^{A} \sigma}(x^{A}), a_{q^{BC}
 \sigma}(x^{BC})\big)\nonumber\\
&=&a^{A||(B||C)}_{q \sigma}(x)
\end{eqnarray}

The synchronous product $A||B$ of two FSA $A$ and $B$ can be
extended to $(A||B)_e$ by taking the synchronous product of the
extended components  $A_e$ and $B_e$. In other words, the
operations extension and product commute, $(A||B)_e=A_e||B_e$.

Moreover, by the above definition of synchronization we now obtain
the following property

\begin{theorem}
   Full synchronous composition of EFA's is an associative
   operation.
\end{theorem}

\noindent \textbf{Proof}: To prove the associativity we
considering three automata $A, A'$ and $A''$, and show that
$(A\|A')\|A'' = A\|(A'\|A'')$. Here, we assume that the three
automata have no common variables.
\newline\newline
\noindent The 8-tuple representing $(A\|A')\|A''$ is
\begin{center}
\begin{tabular}{ll}
  $(A\|A')\|A'' =$ & $\Big \langle (Q \times Q') \times Q'',$\\
  & $ \big(\Sigma \bigcup \Sigma' \big) \bigcup \Sigma'',$\\
  & $\delta^{(A\|A')\|A''},$\\
  & $\big((q_i, q'_i) , q''_i\big),$\\
  & $(Q_m \times Q_m') \times Q_m'',$\\
  & $\big[[X, X'], X'']$\\
  & $G^{(A\|A')\|A''},$\\
  & $\big[[X_m, X'_m], X''_m \big] \Big \rangle$
\end{tabular}
\end{center}

\noindent In order to establish associativity we now have to show
this for each of the elements in the 8-tuple. For the states, the
alphabet, the initial state, the marked states and the variables,
associativity is clear by the laws of set operations. We will now
in turn deal with the guard/action functions and the transition
function.

For the guard functions $g^{(A\|A')\|A''} : X^c \rightarrow
\{\mathrm{true}, \mathrm{false}\}$ of the composite automaton we
have by definition

\begin{equation}
  g^{(A\|A')\|A''}(X^c) = \big[g(X) \wedge g'(X') \big] \wedge g''(X'') = g(X) \wedge \big[g'(X') \wedge g''(X'')] = g^{A\|(A'\|A'')}(X^c)
\end{equation}
\noindent Now consider the action function $a^{(A\|A')\|A''} : X^c
\rightarrow X^c$.
\newpage
\subsection{The translation of an EFA to  an FA}
To simplify the realization we shall restrict us to quite simple
action- and guard functions. For the updating functions we assume
that $a_{q \sigma}(x)=(a^1_{q \sigma}(x),...,a^n_{q
\sigma}(x))=(a^1_{q \sigma}(x_1),...,a^n_{q \sigma}(x_n))$. In
other words, the updating of the variables are independent from
each other. For the guard functions we assume that they are given
in disjunctive normal form $g_{q \sigma}(x)=g^1_{q \sigma}(x)\vee
...\vee g^j_{q \sigma}(x)$. We shall denote the number of "OR"
components $j$ in such an expression by $|g_{q \sigma}|$. These
assumptions makes it straight forward to translate an EFA to an
FA.

@@

Formally we define the synchronous product $A||B$ of two EFA's
$A=\langle Q^A, \Sigma^A, \delta^A, q^A_i, Q^A_m, X^{A}, G^A,X^A_m
\rangle$ and $B=\langle Q^B, \Sigma^B, \delta^B, q^B_i, Q^B_m,
X^{B}, G^B,X^B_m
 \rangle$ as
\begin{eqnarray}
A||B=\langle Q^A\times Q^B, \Sigma^A \cup \Sigma^B , \delta, q_i,
Q^A_m\times Q^B_m, Z, G, Z_m \rangle.
\end{eqnarray}
To define the integer variables, the guard functions, the action
functions and the transition function for the product we make use
of the corresponding elements in $A$ and $B$.

 Let $z^{AB}$ denote the common variables of $x^{A}$ and $x^{B}$, and let $z^A$
and $z^B$ be the distinct variables of $x^{A}$ and $x^{B}$,
respectively. We define the integer variables $z$ of the
synchronous product of $A$ and $B$ as the vector $z=(z^A, z^{AB},
z^B)$. The guard functions $g_{q \sigma}(z)$ are defined as
\begin{eqnarray}\label{guard_sync_2}
g_{q \sigma}(z)=\left\{
\begin{array}{ll}
g_{q^A\sigma}(x^{A})\wedge g_{q^B\sigma}(x^{B}) \textrm{ if }\sigma\in \Sigma^A \cap \Sigma^B\\
g_{q^A\sigma}(x^{A}) \quad\quad \textrm{ if } \sigma\in \Sigma^A \setminus \Sigma^B\\
g_{q^B\sigma}(x^{B}) \quad\quad \textrm{ if }
\sigma\in\Sigma^B\setminus \Sigma^A
\end{array}\right.
\end{eqnarray}
If any one of the guards functions in the above definition are
undefined the guard function for the product $g_{q \sigma}$ is
also undefined. To simplify the notation further, we use "dummy"
guard functions in the following way. If $\sigma\in \Sigma^A
\setminus \Sigma^B$ we introduce fictional guards functions
$g_{q^B\sigma}(.)=1$ for $B$ and if $\sigma\in\Sigma^B\setminus
\Sigma^A$ we set $g_{q^A\sigma}(.)=1$. With this convention we can
write equation (\ref{guard_sync_2}) as
\begin{eqnarray}
g_{q \sigma}(z)= g_{q^A\sigma}(x^{A})\wedge g_{q^B\sigma}(x^{B}).
\end{eqnarray}
To define the action functions for $A||B$ we look at the
restrictions of the updating functions $a^A_\delta$ and
$a^B_\delta$ to the sets $Z^A$ and $Z^B$. The updating functions
are defined as (if $x^{A}$ and $x^{B}$ have no common variables
then $z=(x^{A},x^{B})$)
\begin{eqnarray}\label{action_sync_2}
a_{q \sigma}(z)=\left\{
\begin{array}{ll}
 \big(a^A_{q^A \sigma}(x^{A}), a^B_{q^B \sigma}(z^{B})\big)\quad\quad\sigma\in \Sigma^A \cap \Sigma^B\\
\big(a^A_{q^A \sigma}(x^{A}), z^{B}\big)\quad\quad\quad\sigma\in \Sigma^A \setminus \Sigma^B\\
\big(z^{A}, a^B_{q^B \sigma}(x^{B})\big)\quad\quad\quad\sigma\in
\Sigma^B \setminus \Sigma^A
\end{array}\right.
\end{eqnarray}
As in the definition of the guard functions the notion of being
undefined is inherited from the action functions of $A$ and $B$.
Similar to the "dummy" guard functions we introduce fictional
action functions. If $\sigma\in \Sigma^A \setminus \Sigma^B$ we
introduce fictional action functions $a_{q^B\sigma}(x^B)=x^B$ for
$B$ and if $\sigma\in\Sigma^B\setminus \Sigma^A$ we set
$a_{q^A\sigma}(x^A)=x^A$. If $x^{A}$ and $x^{B}$ have no common
variables then equation (\ref{action_sync_2}), that defines the
action functions of the product, simplifies to
\begin{eqnarray}
a_{q \sigma}(z)=
 \big(a^A_{q^A \sigma}(x^{A}), a^B_{q^B \sigma}(x^{B})\big).
\end{eqnarray}

>>>>

Formally we define the synchronous product $A\|B$ of two EFA's
\begin{eqnarray}
A=\langle Q^A, \Sigma^A, \delta^A, q^A_i, Q^A_m, X^{A},
G^A,x^A_0,X^A_m \rangle
\end{eqnarray} and \begin{eqnarray} B=\langle Q^B, \Sigma^B, \delta^B, q^B_i,
Q^B_m, X^{B}, G^B,x^B_0,X^B_m \rangle
\end{eqnarray} as
\begin{eqnarray}
A\|B&=&\langle Q^A\times Q^B, \Sigma^A \cup \Sigma^B ,
\delta^{A\|B}, (q^A_i,q^B_i) ,\nonumber\\
&& Q^A_m\times Q^B_m, X^A \times X^B, G^{A\|B},(x^A_0,x^B_0),
X^A_m \times X^B_m \rangle.
\end{eqnarray}
To define the guard functions, the action functions and the
transition function of the product we make use of the
corresponding functions in $A$ and $B$. To denote the elements of
$A\|B$ we remove unnecessary  superscripts and write $A\|B=\langle
Q, \Sigma, \delta, q_i, Q_m, X, G ,x_0, X_m \rangle$. The guard
functions $g_{q \sigma}(x)$ are defined as
\begin{eqnarray}\label{guard_sync_1}
g_{q \sigma}(x)=\left\{
\begin{array}{ll}
g_{q^A\sigma}(x^{A})\wedge g_{q^B\sigma}(x^{B}) \quad\quad\sigma\in \Sigma^A \cap \Sigma^B\\
g_{q^A\sigma}(x^{A})\quad\quad\quad\quad\quad\quad\quad\sigma\in \Sigma^A\setminus\Sigma^B\\
g_{q^B\sigma}(x^{B})\quad\quad\quad\quad\quad\quad\quad\sigma\in\Sigma^B\setminus\Sigma^A
\end{array}\right.
\end{eqnarray}
If in any of the three cases, the corresponding guard function is
undefined the guard function for the product $g_{q \sigma}$ is
also undefined. To simplify the notation and increase readability,
we use "dummy" guard functions in the following way. If $\sigma\in
\Sigma^A \setminus \Sigma^B$ we introduce fictional guards
functions $g_{q^B\sigma}(.)=1$ for $B$ and if
$\sigma\in\Sigma^B\setminus \Sigma^A$ we set $g_{q^A\sigma}(.)=1$.
Doing this, we can write equation (\ref{guard_sync_1}) as
\begin{eqnarray}
g_{q \sigma}(x)= g_{q^A\sigma}(x^{A})\wedge g_{q^B\sigma}(x^{B}).
\end{eqnarray}
The updating functions $a_{q \sigma}(x)$ are defined as
\begin{eqnarray}\label{action_sync_1}
a_{q \sigma}(x)=\left\{
\begin{array}{ll}
 \big(a_{q^A \sigma}(x^{A}), a_{q^B \sigma}(x^{B})\big)\quad\quad\sigma\in \Sigma^A \cap \Sigma^B\\
\big(a_{q^A\sigma}(x^{A}),x^{B}\big)\quad\quad\quad\quad\quad\sigma\in\Sigma^A\setminus\Sigma^B\\
\big(x^{A},a_{q^B\sigma}(x^{B})\big)\quad\quad\quad\quad\quad\sigma\in\Sigma^B\setminus\Sigma^A
\end{array}\right.
\end{eqnarray}
As in the definition of the guard functions (\ref{guard_sync_1}),
the notion of being undefined is inherited from the action
functions of $A$ and $B$. Similar to the "dummy" guard functions
we introduce fictional action functions. If $\sigma\in \Sigma^A
\setminus \Sigma^B$ we introduce fictional action functions
$a_{q^B\sigma}(x^B)=x^B$ for $B$ and if
$\sigma\in\Sigma^B\setminus \Sigma^A$ we set
$a_{q^A\sigma}(x^A)=x^A$. With this convention equation
(\ref{action_sync_1}) simplifies to
\begin{eqnarray}
a_{q \sigma}(x)=
 \big(a_{q^A \sigma}(x^{A}), a_{q^B \sigma}(x^{B})\big).
\end{eqnarray}

 The transition function $\delta^{A\|B}$ is defined from $\delta^A$ and $\delta^B$ as
\begin{eqnarray}
\delta^{A\|B}(q,\sigma,x)=\left\{
\begin{array}{ll}
\big(\delta^A(q^A,\sigma),\delta^B(q^B,\sigma),a_{q \sigma}(x)\big) \quad\quad \sigma\in \Sigma^A \cap \Sigma^B \quad g_{q \sigma}(x)=1\\
\big(\delta^A(q^A,\sigma),q^B,a_{q \sigma}(x)\big) \quad\quad\quad\quad\quad \sigma\in \Sigma^A \setminus \Sigma^B \quad g_{q \sigma}(x)=1\\
\big(q^A,\delta^B(q^B,\sigma),a_{q \sigma}(x)\big) \quad\quad\quad\quad\quad \sigma\in \Sigma^B \setminus \Sigma^A \quad g_{q \sigma}(x)=1\\
\textrm{
undefined}\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
g_{q\sigma}(x)=0
\end{array}\right.
\end{eqnarray}

\subsubsection{Properties of the product}

Consider three EFA's $A$, $B$ and $C$. From the definition of the
synchronization we shall now show that
 $(A\|B)\|C=A\|(B\|C)$ i.e. we have:
\begin{theorem}
   Full synchronous composition of EFA's is an associative
   operation.
\end{theorem}

\noindent \textbf{Proof}: We need to prove that $(A\|B)\|C =
A\|(B\|C)$. Here, we assume that the three automata have no common
variables.
\newline\newline
\noindent The 9-tuple representing $(A\|B)\|C$ is
\begin{center}
\begin{tabular}{ll}
  $(A\|B)\|C =$ & $\Big \langle (Q^{A} \times Q^{B}) \times Q^{C},$\\
  & $ \big(\Sigma^{A} \bigcup \Sigma^{B} \big) \bigcup \Sigma^{C},$\\
  & $\delta^{(A\|B)\|C},$\\
  & $\big((q^{A}_i, q^{B}_i) , q^{C}_i\big),$\\
  & $(Q^{A}_m \times Q^{B}_m) \times Q^{C}_m,$\\
  & $\big[[X^{A}, X^{B}], X^{C}]$\\
  & $G^{(A\|B)\|C},$\\
  & $\big((x^{A}_0, x^{B}_0) , x^{C}_0\big),$\\
  & $\big[[X^{A}_m, X^{B}_m], X^{C}_m \big] \Big \rangle$
\end{tabular}
\end{center}

\noindent In order to establish associativity we now have to show
this for each of the elements in the tuple. For the states, the
alphabet, the initial state, the marked states and the variables,
associativity is clear by the laws of set operations. We will now
in turn deal with the guard/action functions and the transition
function.

For the guard functions and the action functions of the composite
automaton we have
\begin{eqnarray}
g^{(A\|B)\|C}_{q \sigma}(x)&=& g_{q^{AB}\sigma}(x^{AB})\wedge
g_{q^C\sigma}(x^{C})\nonumber\\
&=&g_{q^A\sigma}(x^{A})\wedge g_{q^B\sigma}(x^{B})\wedge
g_{q^C\sigma}(x^{C})\nonumber\\
&=& g_{q^{A}\sigma}(x^{A})\wedge g_{q^{BC}\sigma}(x^{BC})\nonumber\\
&=& g^{A\|(B\|C)}_{q \sigma}(x)
\end{eqnarray}
and
\begin{eqnarray}
a^{(A\|B)\|C}_{q \sigma}(x)&=&
 \big(a_{q^{AB} \sigma}(x^{AB}), a_{q^{C}
 \sigma}(x^{C})\big)\nonumber\\
&=&\big(a_{q^{A} \sigma}(x^{A}), a_{q^{B}
 \sigma}(x^{B}), a_{q^{C}
 \sigma}(x^{C})\big)\nonumber\\
&=&\big(a_{q^{A} \sigma}(x^{A}), a_{q^{BC}
 \sigma}(x^{BC})\big)\nonumber\\
&=&a^{A\|(B\|C)}_{q \sigma}(x).
\end{eqnarray}
This shows that $G^{(A\|B)\|C}=G^{A\|(B\|C)}$, and since the
transition function for the standard $FA$ is associative it
follows that $\delta^{(A\|B)\|C}=\delta^{A\|(B\|C)}$.
\begin{flushright}$\square$\end{flushright}

The synchronous product $A\|B$ of two FSA $A$ and $B$ can be
extended to $(A\|B)_e$ by taking the synchronous product of the
extended components  $A_e$ and $B_e$. In other words, the
operations extension and product commute, $(A\|B)_e=A_e\|B_e$.

\subsection{The translation of an EFA to  an FA}
To simplify the realization we shall restrict us to quite simple
action- and guard functions. For the updating functions we assume
that $a_{q \sigma}(x)=(a^1_{q \sigma}(x),...,a^n_{q
\sigma}(x))=(a^1_{q \sigma}(x_1),...,a^n_{q \sigma}(x_n))$. In
other words, the updating of the variables are independent from
each other. For the guard functions we assume that they are given
in disjunctive normal form $g_{q \sigma}(x)=g^1_{q \sigma}(x)\vee
...\vee g^j_{q \sigma}(x)$. We shall denote the number of "OR"
components $j$ in such an expression by $|g_{q \sigma}|$. These
assumptions makes it straight forward to translate an EFA to an
FA.

@@

Formally we define the synchronous product $A\|B$ of two EFA's
$A=\langle Q^A, \Sigma^A, \delta^A, q^A_i, Q^A_m, X^{A}, G^A,X^A_m
\rangle$ and $B=\langle Q^B, \Sigma^B, \delta^B, q^B_i, Q^B_m,
X^{B}, G^B,X^B_m
 \rangle$ as
\begin{eqnarray}
A\|B=\langle Q^A\times Q^B, \Sigma^A \cup \Sigma^B , \delta, q_i,
Q^A_m\times Q^B_m, Z, G, Z_m \rangle.
\end{eqnarray}
To define the integer variables, the guard functions, the action
functions and the transition function for the product we make use
of the corresponding elements in $A$ and $B$.

 Let $z^{AB}$ denote the common variables of $x^{A}$ and $x^{B}$, and let $z^A$
and $z^B$ be the distinct variables of $x^{A}$ and $x^{B}$,
respectively. We define the integer variables $z$ of the
synchronous product of $A$ and $B$ as the vector $z=(z^A, z^{AB},
z^B)$. The guard functions $g_{q \sigma}(z)$ are defined as
\begin{eqnarray}\label{guard_sync_2}
g_{q \sigma}(z)=\left\{
\begin{array}{ll}
g_{q^A\sigma}(x^{A})\wedge g_{q^B\sigma}(x^{B}) \textrm{ if }\sigma\in \Sigma^A \cap \Sigma^B\\
g_{q^A\sigma}(x^{A}) \quad\quad \textrm{ if } \sigma\in \Sigma^A \setminus \Sigma^B\\
g_{q^B\sigma}(x^{B}) \quad\quad \textrm{ if }
\sigma\in\Sigma^B\setminus \Sigma^A
\end{array}\right.
\end{eqnarray}
If any one of the guards functions in the above definition are
undefined the guard function for the product $g_{q \sigma}$ is
also undefined. To simplify the notation further, we use "dummy"
guard functions in the following way. If $\sigma\in \Sigma^A
\setminus \Sigma^B$ we introduce fictional guards functions
$g_{q^B\sigma}(.)=1$ for $B$ and if $\sigma\in\Sigma^B\setminus
\Sigma^A$ we set $g_{q^A\sigma}(.)=1$. With this convention we can
write equation (\ref{guard_sync_2}) as
\begin{eqnarray}
g_{q \sigma}(z)= g_{q^A\sigma}(x^{A})\wedge g_{q^B\sigma}(x^{B}).
\end{eqnarray}
To define the action functions for $A\|B$ we look at the
restrictions of the updating functions $a^A_\delta$ and
$a^B_\delta$ to the sets $Z^A$ and $Z^B$. The updating functions
are defined as (if $x^{A}$ and $x^{B}$ have no common variables
then $z=(x^{A},x^{B})$)
\begin{eqnarray}\label{action_sync_2}
a_{q \sigma}(z)=\left\{
\begin{array}{ll}
 \big(a^A_{q^A \sigma}(x^{A}), a^B_{q^B \sigma}(z^{B})\big)\quad\quad\sigma\in \Sigma^A \cap \Sigma^B\\
\big(a^A_{q^A \sigma}(x^{A}), z^{B}\big)\quad\quad\quad\sigma\in \Sigma^A \setminus \Sigma^B\\
\big(z^{A}, a^B_{q^B \sigma}(x^{B})\big)\quad\quad\quad\sigma\in
\Sigma^B \setminus \Sigma^A
\end{array}\right.
\end{eqnarray}
As in the definition of the guard functions the notion of being
undefined is inherited from the action functions of $A$ and $B$.
Similar to the "dummy" guard functions we introduce fictional
action functions. If $\sigma\in \Sigma^A \setminus \Sigma^B$ we
introduce fictional action functions $a_{q^B\sigma}(x^B)=x^B$ for
$B$ and if $\sigma\in\Sigma^B\setminus \Sigma^A$ we set
$a_{q^A\sigma}(x^A)=x^A$. If $x^{A}$ and $x^{B}$ have no common
variables then equation (\ref{action_sync_2}), that defines the
action functions of the product, simplifies to
\begin{eqnarray}
a_{q \sigma}(z)=
 \big(a^A_{q^A \sigma}(x^{A}), a^B_{q^B \sigma}(x^{B})\big).
\end{eqnarray}
